\documentclass{article}% can change for artical or book etc
\usepackage{graphicx}
\usepackage{verbatim}% for also need this for multiple comment
\usepackage{microtype}% its for underline to break
\usepackage{fontspec}% Bangla font can allow for 
\usepackage[a4paper, top=2.0cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}% A4 size page
\usepackage[normalem]{ulem}% underline for 
\usepackage{paralist}% paragraph type item
\usepackage{enumitem}% Alphabetic big letter use for package
\usepackage{url,hyperref}% link attach for using
\begin{comment}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Beauty of Jesus}
\chead{Inspire}
\rhead{1}

\lfoot{Contact Email:engilazarus10@gmail.com}
\cfoot{}
\rfoot{Know GOd}
\end{comment}
%\usepackage[utf8]{inputenc} % can be change if use graphics nothing change that i see but i dont know
\emergencystretch=3em

\newfontfamily\bangla{Kalpurush}[Script=Bengali]
\title{Planning for myself}
\author{Lazarus Tuwary Tripura}
\date{5 July 2026}

\begin{document}

\maketitle
\vspace{-8mm}
\begin{center}
    \textbf{Lazarus you have to change your Habit. \\
    Without it never going to change your life.}
\end{center}


\section{Introduction}
\begin{comment} its for multiple comment and connected with usepackage verbatim.
    Do you know why i hate my life, why i am really want to die because iam not satisfy with what iam being continuous habitual fact. So why it need be mutable with willpower and stand strong.
\end{comment}
Life is a long process of learning method. \\ That is, you cannot get by one day or two days,
you have to think about everything and cope with the situation through it.
\section{Emotion immersion}
About Nothing in earth but in God is something. Because possible in God who can anything.
\subsection{sorrow}
%\tiny{yes, became tiny("-")}

\small{Sorrow And Feeling Like "Nothing"\\
When a massive failure strikes, it evaporates your confidence, leaving a hollow sensation that you or your efforts amount to absolutely nothing. }
\\
\huge
"My flesh and my heart may fail, but God is the strength of my heart and my portion forever."
— Psalm 73:26
\small
\subsection{Failure}
failure has lessons, but let’s be honest: when you are right in the thick of it, hearing "it’s a learning experience" feels incredibly hollow. It hurts, and it is completely normal to just be upset about it first. Once the initial sting softens a bit, failure actually exposes things that success completely hides. Success makes us think we have it all figured out, but failure is a brutal, honest teacher.
\subsection{Nothing}
\footnotesize
When you have nothing left to prove, you are finally free. The pressure to perform for an audience or defend your pride is gone. Failure loses its power to destroy you because your identity is no longer tied to an outcome. You can stop striving and simply exist.\small \textit{"I care very little if I am judged by you or by any human court; indeed, I do not even judge myself... It is the Lord who judges me."
— 1 Corinthians 4:3–4}

\subsection{Anger}
Anger And Bitterness
If left untended, that deep sorrow fast-tracks into anger at how things turned out, which eventually hardens into a cold, bitter outlook toward life or the people around you.
\textbf{"When my heart was grieved and my spirit embittered, I was senseless and ignorant; I was a brute beast before you. Yet I am always with you; you hold me by my right hand."
— Psalm 73:21–23}

\subsection{bitter}
Bitterness promises to protect you, but it actually keeps you in a state of constant war.
When you get hurt, bitterness acts like an emotional shield. It feels powerful because it is fueled by anger, and it tells you, \underline{"If I stay angry and cold, no one can catch me off guard or hurt me like this again."}
But bitterness cannot give you calm for two reasons:
It keeps the trauma alive: Calm requires rest. Bitterness requires you to constantly replay the failure or the hurt in your mind to keep the anger hot. You are essentially re-wounding yourself every single day to keep the shield up.
It is an active defense mechanism: True calm is a relaxed state. Bitterness is an alert state—it is your emotional guard dogs barking at the gate 24/7. You cannot find peace while you are actively defending a fortress.
To get calm, you eventually have to lay the shield down. Not because what happened was okay, but because you deserve to rest. \large \textbf{\textit{"Get rid of all bitterness, rage and anger, brawling and slander, along with every form of malice."
— Ephesians 4:31}}
\section{Dream} % for use percentage so slash need
Every dream take time, effort, shame, criticism but did you take any kind of so, how you think you can becoming like someone. With a global population of around 8 billion people, and only about 3,000 billionaires on Earth, the raw percentage of becoming a standard billionaire is roughly 0.000037\% But reaching the level of Elon Musk—who is a Trillionaire with a net worth hovering near \$1 trillion—is entirely different. There is only one person at that level out of 8 billion. this \copyright \ from chatpt and \textregistered \ here. My life is like this \# \\
Before my dream have such as:
\begin{itemize} % for Bullet point
    \item Adventure
    \item Dancer
    \item Teacher
    \item Pastor
    \item Preacher
    \item Wealthy Man
    \item Best Farmer
    \item Doctor
    \item All Rounder Engineer in every field
    \item Scientist
    \item CEO of Company
    \item Entrepreneur 
\end{itemize}
But in present everything become zero. Only that option i have:
\begin{enumerate}
    \item Trust in God % number inside bullet point
    \\ex: \begin{inparaenum}[(i)] % for again using enumerate here
        \item Abraham
        \item Joseph
        \item Job
        \item Moses
    \end{inparaenum}
    \begin{itemize}
        \item Pray Regularly
        \item Be Patient With Timing
        \item Trust During Difficult Times
        \item Avoid Negative Influences
        \item Develop Discipline
        \item Keep Hope Alive
    \end{itemize}
    \item Pray to God
    \\ex:
    \begin{inparaenum}[(1)]
            \item Daniel
            \item Hannah
            \item Elijah
            \item Jonah
    \end{inparaenum}
    
    \begin{itemize}
        \item Start With Gratitude
        \item Speak Honestly
        \item Ask for Guidance
        \item Confess Mistakes
        \item Stay Humble
        \item Trust God’s Timing
    \end{itemize}
    \item Fully surrender to God
    \\ex:
    \begin{inparaenum}[(1)]
        \item Jesus Christ
        \item Mary
        \item Noah
        \item Isaiah
    \end{inparaenum}
    \begin{itemize}
        \item Accept That God Knows Better
        \item Give Your Worries to God
        \item Remove Harmful Habits
        \item Remain Thankful
        \item Keep Returning to God Daily
    \end{itemize}
    \item Pray everyday
    \\ex: 
    \begin{inparaenum}[(1)]
        \item David
        \item Nehemiah
        \item Samuel
        \item Ezra
    \end{inparaenum}
    \begin{itemize}
        \item Begin the Day With Prayer
        \item Set a Daily Prayer Time
        \item Pray for Other People
        \item Read Scripture Alongside Prayer
        \item Ask for Wisdom and Discipline
    \end{itemize}
\end{enumerate}
\section{Delight}
{\bangla আমার জীবন যদিও শূন্য মনে হয়, আমার ভবিষ্যৎ যদিও অস্পষ্ট দেখায়, আর আমার শক্তি যদিও একদম কমে যায়; এমনকি আমার যদি কোনো বিকল্প পরিকল্পনা (ব্যাকআপ প্ল্যান) না থাকে, আশেপাশে কোনো সাহায্য না থাকে, আর এখন পর্যন্ত চোখের সামনে কোনো ভালো ফলাফল নাও দেখা যায় তাও যে ঈশ্বর আমাকে রক্ষা করেছেন, তিনিই আমার আনন্দ! জীবন যতই শুষ্ক মনে হোক না কেন, আমি তাও আনন্দ করব, কারণ ঈশ্বরই আমার পরিত্রাণ এবং আমার শক্তি। আমার হাতে যদি কিছু নাও থাকে এবং নিজেকে যদি একা মনে হয়, সবার চেয়ে পিছিয়ে পড়া আর প্রচণ্ড চাপের মধ্যে মনে হয়, তাও আমি ঈশ্বরেই আনন্দ করব। কারণ তাঁর ওপর আমার বিশ্বাস আছে। কারণ ঈশ্বর আমাকে তার পরিকল্পনার অংশ করেছে এবং একদিন সময় আসবে।}\\
Modern Era People Who Delighted in God:-
\begin{enumerate}[label=\Alph*.] % can use here [label=\roman*., start=3]
    \item Billy Graham
    \item Mother Teresa
    \item Nick Vujicic
    \item Corrie ten Boom
\end{enumerate}
\begin{flushright}
    Mood is a liar:\\
    If i wait until i feel like it, \\
    i will never start.
\end{flushright}
\begin{flushleft}
    Regret vs. Self-Discipline: \\
    Choose which weight you want to carry today.\\
    Self-discipline weighs ounces; regret weighs tons.
\end{flushleft}
\begin{center}
    Future I:\\
    In an hour, am i going to be glad i started, \\
    or pissed off that i wasted time?
\end{center}
\uline{" Amateurs sit and wait for inspiration, the rest of us just get up and go to work" -Stephen king. So stop scrolling, Close this tab, Go----------}
\\\href{https://www.youtube.com/}{Do you Want to go? Have to press and search}% for use href and url need usepakage about
\\But if you want to specific to hear for i recommend this link \\\url{https://youtu.be/zbKXkpiLcfk}

\end{document}
